---
title: "Lab 11 - Tests of Hypotheses Part 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab 11 - Tests of Hypotheses Part 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ROSAlab11)
```

# Introduction 

This package contains a wonderful function which produces a histogram and an output named list containing, among other items, the confidence interval and the critical t-values.

# The Function - `ciNonSym`

To show this function off, we will examine the `Length` data from the `DDT` data set.

```{r, fig.align = "center", fig.width=7, fig.height=5}
library(ggplot2)

l <- ciNonSym(x = ddt$LENGTH, 
                        alpha = 0.05,
                        alpha2 = 0.02, 
                        mu0 = 45, 
                        epsilon = 4,
                        bins = 25)

l
```

# Shiny App - `shinyfishies`

# `shinytrains`

To view the app, run the following code in an active `R` session.

`shiny::runGitHub(repo = "MATH4753ROSAlab11", username = "brandanrosa", subdir = "inst/shinyfishies")`
















